Something that surprised me about {\it Frankenstein} by Mary Shelley
was how quickly Frankenstein's monster was created in the story.
In movies about the book the creation of the monster was
the climax of the film, but for the book it was more of a plot
point.

Volume one starts with a few letters from R. Walton
directed to his sister in England describing how on
an expedition to Antarctica they found a man on a sled
and brought him aboard. This transitions into an account
from the saved man, Victor Frankenstein about his life
before his "tragedies."

Victor moves to Ingolstadt to attend university and takes up
natural sciences like chemistry and other natural philosophies.
Victor exceeds the expectations of his professors and starts
working on his personal project above his apartment. He neglects
is health and family for the purpose of creating his monster.
Only after the monster is given life does Victor realize his mistake
and is bedridden from fear of the thing. A old friend nurses Victor
to health and Victor must return to his home for the murder of his
youngest brother William at what he believes is the hands of his monster.
The judges believe that another childhood friend of his, Justine is the
one who murdered his brother and she is sentenced to death after
confessing under the threat of "excommunication and hell fire."

Volume one ends with Victor having created his monster and condeming
two of his closest friends to death. He cannot prove Justine's
innocence because the tale would be that of a madman and no one would
believe him. So Victor has to suffer in silence that he is the creator
of William and Justine's death.