\section{Chapter 1 Questions}
\subsection{Short Answer}
\begin{enumerate}
    \item If you have been contracted to perform an attack against a target system, you are what type of hacker?\\White hat.
    \item Which of the following describes an attacker who goes after a target to draw attention to a cause?\\Hactivist.
    \item What level of knowledge about hacking does a script kiddie have?\\Low.
    \item Which of the following does an ethical hacker require to start evaluating a system?\\Permission.
    \item A white-box test method means the tester has which of the following?\\Complete information of system / network.
    \item Which of the following describes a hacker who attacks without regard for being caught or punished?\\Suicide Hacker.
    \item What is a code of ethics?\\A description of expected behavior.
    \item The group anonymous is an example of what?\\Hacktivists.
    \item Companies may require a penetration test for which of the following reasons?\\Regulatory reasons, IT audit, Network performance.
    \item What should a pen-tester do prior to initiating a new penetration test?\\Get permission.
    \item Which of the following best describes what a hacktivist does?\\Hacks for political / ideological reasons.
    \item Which of the following best describes what a suicide hacker does?\\Hacks without stealth.
    \item Which type of hacker may use their skills for both benign and malicious goals at different times?\\Gray Hat.
    \item What separates a suicide hacker from other attackers?\\Lack of fear of being caught.
    \item Which of the following would most likely engage in the pursuit of vulnerability research?\\White Hat.
    \item Vulnerability research deals with which of the following?\\Passively uncovering vulnerabilities / weaknesses.
    \item How is black-box testing performed?\\With no knowledge.
    \item A contract is important because it does what?\\Gives proof of  permission.
    \item What does TOE stand for?\\Target of evaluation.
    \item Which of the following best describes a vulnerability?\\Weakness (in a system).
    \item What is the most important aspect when conducting a penetration test?\\Recieving formal written agreement, Documenting all actions and activities and maintaining proper handoff with the information assurance team, remediating serious threats immediately
    \item Some detail of target system is what kind of assessment?\\Gray box testing.
    \item A team that conducts penetration testing can be refereed to as what?\\Red team.
    \item Which of the following organizations provides government-backed standards?\\NIST (National Institute of Standards and Technology).
    \item Which term best describes the several hacking attacks in sequence?\\Daisy Chaining.
    \item A penetration tester is which of the following?\\A security professional who's hired to break into a network to discover vulnerabilities.
    \item How can you find out which computer crim law are applicable in your state?\\contact you local law enforcement agencies.
    \item What organization offers the CEH certification exam?\\EC-Council
    \item A written contract isn't necessary when a friend recommends a client?\\False
\end{enumerate}

\subsection{Long Answer}
\begin{enumerate}
    \item What is Ethical hacking? Who are Hackers? Describe types of Hackers.\\
    Ethical hacking is breaking into a system with the owners permission to report on the weaknesses of the system to correct unsecured applications as well as analyze a companies security policy and procedures for industry regulations.
    Hackers are categorized by their skill and intent.
    Black hat hackers are criminals that illegally break into systems, White hat hackers follow a code of ethics to separate themselves from black hat hackers.
    Gray hat hackers could be good or bad and should not be fully trusted.
    Suicide hackers are not worried about stealth because they do not fear prison time.
    Script kiddies require the lowest skill and do not understand most of what they do. 
    \item Describe tasks of the penetration tester.\\
    Once receiving a contract, the penetration tester will follow 7 phases, footprinting, scanning, enumeration, system hacking, privilege escalation, planting backdoors, and covering tracks, where the last 4 could be lumped into one 'hacking' task.
    After assessing the security of the system, the tester will prepare a report of everything they found to be presented to the client.
    Depending on the contract the tester could have to also give remedial recommendations or perform the remediation themselves.
    \item Why Companies / organizations need penetration testers?\\
    Security is becoming more important with the increased access to personal data.
    Penetration testers ensure compliance with industry laws such as HIPPA and to keep the IT staff from becoming to complacent.
    Hackers are finding new vulnerabilities and the IT team needs to be assured that their data is secure.
    Monitor networks.
    \item Describe Pen-testing methodologies.\\
    Using a black box methodology, the penetration tester is not given any information about the network topology or devices / services in use.
    The tester will have to find out as much as they can from outside the network before attempting to break into it.
    With a white box model, the pen tester is given all crucial information about the system such as network topology, devices, operating systems and staff. 
    \item Describe phases of Pen testing process.\\
    Footprinting is the initial phase of the penetration test where the tester gathers as much information about the system from the outside, ip addresses of servers and users, what operating systems are on which machines, domain information from websites.
    The scanning phase is a deeper look into the data gathered from footprinting, which ports are open on what machines.
    Enumeration establishes an active connection to the target hosts to discover potential attack vectors in the system, gathering usernames, group names, hostnames, network shares and services.
    Next the pen tester can start hacking using the data that has been gathered.
    \item Describe detail on any two certification exams available in industry, that prepare you for jobs in domain of 'ethical hacking'.\\
    The OSCP is the offensive security certified professional, which teaches network and application exploits, buffer overflows, data manipulation scripts and hands on system exploits.\\
    The Certified Ethical Hacker course developed by the International Council of Electronic Commerce Consultants (EC-Council) covers 22 subject areas 
\end{enumerate}