\section{Chapter 4}
\subsection{Short Answer}
\begin{enumerate}
    \item Which of the following best describes footprinting?\\Investigation of a target.
    \item Which of the following is not typically used during footprinting?\\Port Scanning.
    \item Why use Google Hacking?\\To fine tune search results.
    \item Which of the following is natively installed on *nix OS systems to conduct DNS queries?\\Dig.
    \item What is EDGAR used to do?\\Chech financial files.
    \item Which of the following can be used to tweak or fine-tune search results?\\Operators.
    \item Which of the following can an attacker use to determine the technology and structure within an organization?\\Job boards.
    \item Which of the following can be used to assess physical security?\\Street views.
    \item Which of the following can help you determine business processes of your target through human interaction?\\Social Engineering.
    \item The Wayback Machine is used to do which of the following?\\View archived versions of websites
    \item Which record will reveal information about a mail server for a domain?\\MX.
    \item Which tool can be used to view web server information?\\Netcraft.
    \item what can be configured in most search engines to monitor and alert you of changes to content?\\Alerts.
    \item What phase comes after footprinting?\\Scanning.
    \item If you can't gain enough information directly from a target, what is another option?\\Competitive analysis.
    \item Which of the following provides free information about a website that includes phone numbers, administrator's email, and even domain registration authority?\\\url{lookup.icann.org}
    \item Which of the following would be a very effective source of information as it relates to people's personal and contact information?\\Social networking.
    \item Footprinting can determine all of the following except \verb|_____|?\\Detail business distribution and number of personnel.
    \item Footprinting has mainly two types. What are they?\\Active and passive.
    \item Which tool can trace the path of a packet?\\\verb|tracert|.
    \item What does the TTL value mean?\\Time to leave : packet remaining live until it times out.
    \item What information does the traceroute tool provide?\\Route path information an hop count.
    \item Which of the following acronyms represent the institution that governs / tracks North American IP space?\\ICANN.
    \item What phase of hacking is: gathering publicly available information, staking out the facility, observing workers as they enter and leave?\\Passive reconnaissance.
    \item What program can be used to discover firewalls.\\Traceroute.
    \item what DNS record type provides the port and services the server is hosting?\\SRV (service record).
    \item You see the following text written down -- Port:502. What does that likely reference?\\Shodan search.
    \item What would you be looking for with the following Google query? \verb|filetype:txt administrator:500:|\\Text files including the text 'administrator:500:'
\end{enumerate}

\subsubsection{Long Answer}
\begin{enumerate}
    \item What is footprinting. What information can be gathered using the footpringing process?
    \item Describe types of footprinting, with examples.
    \item Write on \enquote{Offline website downloading and analyzing} - Tools / utilities available and in use.
    \item How Google hacking can be useful for footprinting process.
    \item Write at lease 3 examples of Operators / Queries within google hacking.
    \item Write on Tools / utilities / websites useful for gathering PII of target people, with example.
\end{enumerate}