\textquote{Brown v.\ Board of Education} was the most impactful case in American history in regards to the social, political, and economic fabric of the nation. \autocite{melvin}
The ruling of \textquote{Brown v.\ Board of Education of Topeka} did not immediately remove the racial segregation established with \textquote{Plessy v.\ Ferguson} in 1896.
The case protected the rights of minorities, meaning to reverse the ruling of the \textquote{Plessy v.\ Ferguson} case.
I believe that the case both presents a new precedent and enforces an older idea.
The new idea the case presents is that everyone should have the right to a proper education and should not be forced to travel long distances and deal with unsavory conditions when there are more favorable ones available.
The older idea being that \textquote{all men are created equal} is also enforced, it is just also being applied to African Americans as well.

The response to the decision was split between the north and the south.
\textquote{Northerners hailed the decision as \textquote{momentous.}} \autocite{melvin}
Whereas the south started to opposed the decision after they realized that the court would not be overturning the decision.
White Citizens Councils began forming for \textquote{total war} in defence of segregation as they waited for the courts plan of implementation.
Black communities were apprehensive about the decision.
They felt that the decision was a step in the right direction but did not know how the plan was to be implemented or how the more zealous groups would respond.