In order to analyze the \textquote{Brown v.\ Board of Education of Topeka} supreme court case, we must first understand some previous developments.
The Fourteenth Amendment, section 1 states that \textquote{No State shall \dots deny any person within its jurisdiction the equal protection of the laws.} \autocite{14th} Meaning, that states could not treat whites and non-whites differently under the law.
Another supreme court case that was important to the decision of \textquote{Brown v.\ Board of Education of Topeka} was the \textquote{Plessy v. Ferguson} case of 1896.
This case ruled that the segregation of blacks and whites was constitutional, but only when both parties had access to the same quality of resources.
The \textquote{Plessy v. Ferguson} case essentially cemented the idea of \textquote{separate but equal}.\autocite{plessy}

In 1954 the supreme court case \textquote{Brown v.\ Board of Education of Topeka,} where a conglomeration of similar cases from four different states would overturn the ruling of \textquote{Plessy v. Ferguson}.
The plaintiff of each of the cases were seeking \textquote{admission to the public schools of their community on a nonsegregated basis} \autocite{brown} but were denied because of segregation laws.
The plaintiffs argued \textquote{that segregated public schools are not \textquote{equal} and cannot be made \textquote{equal,} and that hence they are deprived of the equal protection of the laws.} \autocite{brown}

The supreme court unanimously decided against school segregation because of the inability of schools to provide equal care to whites and non-whites and the psychological effects of segregation on colored children.
The decision in \textquote{Brown v.\ Board of Education of Topeka} believed that \textquote{separate but equal} had no place in education.
The combination of laws and funding that enforce attendance in schools means that we should be giving everyone as good of an education as possible.
This decision to desegregate schools would have a considerable impact on the lives of many Americans and continue to push the civil rights movement.