The United States continued its isolationist views until the bombing of Pearl Harbor in December of 1941.
Charles A.\ Lindbergh and the American First Committee advocating \textquote{America First}, were staunch believers in American isolationism.
Lindbergh was the first person to complete a solo, non-stop, trans-Atlantic flight, and used his fame to persuade the American people against entering into the war.
Lindbergh, and the America First Committee believe that the defence of America should come first and foremost, saying, \textquote{We must turn our eyes and our faith back to our own country before it is too late.}
Even if we did as suggested by Lindbergh and build up Americas defences, we would still eventually have to deal with the Nazi's eventually, or they would invade as they did many other countries.

The idea of isolationism in America goes as far back as Washington and the Monroe Doctrine, Washington thought that meddling in other nations affairs would be harmful to America.
While the idea of isolationism is good, with how fast the Axis powers were taking control of Europe, the problem of war would soon be on Americas doorstep.

The Atlantic Charter outlined the idealized vision for political and economic order of the postwar world.
Signed by Roosevelt and Churchill on August 14, 1941, this document was a major shift the in the ideology of the United States.
The prevailing belief of isolationism began to give way to interventionism.
The third principle outlined in the Atlantic Charter is probably the most important for interventionism stating, \textquote{Third, they respect the right of all peoples to choose the form of government under which they will live; and they wish to see sovereign rights and self-government restored to those who have been forcibly deprived of them.}
While many still supported the America First Committee,
Roosevelt proceeded to provide non-military aid to nations targeted by Axis powers.

Before the bombing of Pearl Harbor, the majority of Americans wanted as little to do with the war as possible.
After Perl Harbor, Americans were devastated and wanted retribution.