\section{Chapter 3}
\subsection{Long Answer}
\begin{enumerate}
    \item Describe general forensics methodologies\\
    Handle original data as much as possible, comply with rules of evidence, avoid exeding ones knowledge, create an analysis plan,
    \item write on File slack searching
    \item Describe forensics evidence - gathering measures.\\
    Avoid changing evidence, determine evidence creation, trust only physical evidence, search though a device, present evidence well.
    \item List any 5 skills, that claim by CHFI, will have with certified professional.\\eccouncil.org
    \item Write features of 2 forensics tools
    \item Describe how to set up a forensic lab.
\end{enumerate}

\subsection{Short answer}
\begin{enumerate}
    \item To preserve digital evidence, an investigator should?\\Make two copies of each evidence item using different imaging tools.
    \item A simple DOS copy will not include deleted files.
    \item only one
    \item The MD5 message-digest algorithm is used to \verb|____|\\hash a disk to verify that a disk is not altered when you examine it.
    \item What is the most important reason that you do not touch the actual original evidence any more than you have to?\\Each time you touch digital data, there is some chance of altering it.
    \item Rules of evidence.
    \item Forensic investigators who collect data as evidence must understand the \verb|___| of information, which refers to how long it is valid.\\life span
    \item us of \verb|_____| enables an investigator to reconstruct file fragments if files have been deleted or overwritten.\\bit-level tools.
    \item What is the purpose of hashing a copy of a suspect drive?\\To check for changes.
    \item The unused space between the logical end of file and the physical end of file is known as \verb|_____|\\ File slack.
    \item \verb|______| sets standards for digital evidence processing, analysis, and diagnostics.\\The American Society of Crime Laboratory Directors.
    \item When gathering system evidence, what is NOT a common principle?\\Trust only virtual evidence.
    \item One principal of evidence gathering is to avoid changing the evidence. Which of the following is NOT true of evidence gathering?\\Photograph seized equipment after you set it up in the lab.
    \item AccessData certified examiner.
\end{enumerate}