\section{Chapter 2}
\subsection{Long answer}
\begin{enumerate}
    \item Describe how computer crime \enquote{Identity theft} affects forensics.\\
    Phishing, spyware, discarded information.
    First the investigator should check for spyware 
    \item Describe how computer crime \enquote{Hacking systems for data} affects forensics.\\
    SQL injection - check firewall and database logs for connection information.
    Cross-site scripting - Look for scripts not coded by websites programmers, search web server logs.
    Password cracking - Check system logs for reboots followed by administrative logins, physical security.
    Trick tech support - Search system for unrecognized scripts in startup folders, examine usage of compromised account.
    \item Describe how computer crime \enquote{Internet / computer fraud} affects forensics.\\
    Begin tracing communications and financial transactions.
    Data piracy investigations should trace owners of the domains distributing intellectual property.
    \item Describe how computer crime \enquote{Non-access computer crime} affects forensics.\\
    Check packet data for source addresses (MAC) or for related information 
    \item Describe how computer crime \enquote{Cyberstalking - harrasement} affects forensics.\\
    Trace emails and phone records.
\end{enumerate}

\subsection{Short answer}
\begin{enumerate}
    \item When investigating a virus, what is the first step?\\Document the virus.
    \item Which of the following crimes is most likely to leave email evidence?\\Cyberstalking.
    \item Where would you seek evidence that \textit{ophcrack} (or similar password cracking tool) had been used on a Windows server 2008 machine?\\In the logs of the server; look for the reboot of the system.
    \item Logic bombs are often perpetrated by who?\\Disgruntled employees.
    \item What is the primary reason to take cyberstalking seriously?\\It can be a prelude to real-world violence.
    \item What is the starting point for investigating in DoS attacks?\\Tracing the packets.
    \item Spyware.
    \item With respect to fishing, a good ficticious email gets a \verb|______| response rate, according to the Federal Bureau of Investigation (FBI).\\1 to 3 percentage.
    \item \verb|_____| refers to phishing with a specific, high-value target in mind.\\Whaling
    \item Cross-site scripting (XSS).
    \item Which of the following are subclasses of fraud?\\Investment offers and data piracy.
    \item Cyberstalking
    \item Identity theft
    \item 
\end{enumerate}