\begin{problem}{\#1 (15 points)}
    Construct a regular expression defining each of the following languages over the alphabet \(\Sigma=\{a,b\}\):
    \begin{enumerate}[label=\alph*)]
        \item The language of all words that do not begin with \(ba\).
        \item The  language  of  all  words  in  which  the  total number of b’s is divisible by 3 no matter how they are distributed, such as \(bbabbaabab\).
        \item All words that contain exactly 2 b’s or exactly 3 b’s, not more.
        \item All words in which \(a\) appears tripled, if at all. This means that  every  clump of a’s contains 3 or 6 or 9 or 12 \ldots\ a’s.
        \item All words that contain at least one of the strings \(S_1,S_2,S_3, \text{or} S_4\).
    \end{enumerate}
\end{problem}
\vspace{2em}
\begin{solution}
    \begin{enumerate}[label=\alph*)]
        \item \(a^*b^*\)\\Contains only a's or only b's or a's followed by b's, therefore the string \(ba\) should never appear.
        \item \((a^*ba^*ba^*ba^*)^*\)
        \item \(a^*(b+\Lambda)a^*ba^*ba^*\)
        \item \(b^*(aaa)^*b^*\)\\Nothing was said about there being no a's so \((aaa)^*\) allows for only strings of b's or an empty string.
        \item \((S_1+S_2+S_3+S_4)(S_1+S_2+S_3+S_4)^*\)
    \end{enumerate}
\end{solution}

\begin{problem}{\#2 (15 points)}
    Construct   a   regular   expression   defining   each   of   the following languages over the alphabet \(\Sigma=\{a,b\}\):
    \begin{enumerate}[label=\alph*)]
        \item All strings that end in a double letter.
        \item All strings that do not end in a double letter.
        \item All strings that have exactly one double letter in them.
        \item All words in which the letter \(b\) is never tripled. This means that no word contains the substring \(bbb\).
        \item All words in which \(a\) is tripled or \(b\) is tripled, but not both. This means each word contains the substring \(aaa\) or the substring \(bbb\) but not both.
    \end{enumerate}
\end{problem}
\vspace{2em}
\begin{solution}
    \begin{enumerate}[label=\alph*)]
        \item \((a+b)^*(aa+bb)\)
        \item \((a+b)^*(ab+ba)+a+b+\Lambda\)
        \item \((b+\Lambda)(ab)^*aa(ba)^*(b+\Lambda) + (a+\Lambda)(ba)^*bb(ab)^*(a+\Lambda)\)
        \item \((\Lambda+b+bb)(a+ab+abb)^*\)
        \item \((\Lambda+b+bb)(a+ab+abb)^*aaa(\Lambda+b+bb)(a+ab+abb)^*+\\(\Lambda+a+aa)(b+ba+baa)^*bbb(\Lambda+a+aa)(b+ba+baa)^*\)
    \end{enumerate}
\end{solution}

\begin{problem}{\#3 (10 points)}
    Let us consider the regular expression
    \[(a+b)^*a(a+b)^*b(a+b)\]
    Show that this is equivalent to
    \[(a+b)^*ab(a+b)^*\]
    In the sense that they define the same language.
\end{problem}
\vspace{2em}
\begin{solution}
    \((a+b)^*=\{\Lambda,a,b,aa,ab,bb,aaa,aab,aba,abb,bbb,\ldots\}\)\\
    \(a(a+b)^* = \{a,aa,ab,aaa,aab,aba,\ldots\}\)\\
    \(b(a+b) = \{ba,bb\}\)\\
    \\
    \((a+b)^* = \{\Lambda,a,b,aa,ab,bb,aaa,aab,aba,abb,bbb,\ldots\}\)\\
    \(ab(a+b)^* = \{ab,aba,abb,abaa,abab,abbb,\ldots\}\)\\
    \\
    \(a(a+b)^*b(a+b) = ab(a+b)^*\)
\end{solution}

\begin{problem}{\#4 (5 points)}
    If the only difference between \(L\) and \(L^*\) is the word \(\Lambda\), is the only difference between \(L^2\) and \(L^*\) the word \(\Lambda\)?
    Show by example.
\end{problem}
\vspace{2em}
\begin{solution}
    No, if \(L=\{a,b,aa,ab,ba,bb,\ldots\}\) then \(L^*=\{\Lambda,a,b,aa,ab,ba,bb,\ldots\}\).\\
    But \(L^2=\{aa,bb,aaaa,abab,baba,bbbb\}\) which does not include \(\{a,b\}\).
\end{solution}

\begin{problem}{\#5 (12 points)}
    Describe in English phrases the languages associated with the following regular expressions.
    \begin{enumerate}[label=\alph*]
        \item \((a+b)^*a(\Lambda+bbbb)\)
        \item \((a(a+bb)^*)^*\)
        \item \(a(aa)^*b(bb)^*\)
        \item \(((a+b)a)^*\)
    \end{enumerate}
\end{problem}
\vspace{2em}
\begin{solution}
    \begin{enumerate}[label=\alph*]
        \item The set of strings over the alphabet \(\{a,b\}\) that ends with \(a\) or \(bbbb\) and must have at least one \(a\).
        \item The set of strings over the alphabet \(\{a,b\}\) with any number of a's followed by none or even numbers of \(b\)'s.
        \item The set of strings over the alphabet \(\{a,b\}\) that contains only odd numbers of \(a\)'s followed by odd numbers of \(b\)'s
        \item The set of strings over the alphabet \(\{a,b\}\) with any number of \(a\)'s or \(b\)'s ending with an a ($\Lambda$ included)
    \end{enumerate}
\end{solution}