\section{Scanning}
\subsection{What is Scanning}

Scanning is a process that involves engaging and probing a target network with the intent of revealing useful information of networks and systems.
Combined with the information from footprinting, it is possible to get a decent picture of a target organization network-map.

With the rapid growth of networks and turnover of personnel, scanning can sometimes give a better network graph that the client can provide.


\subsection{Types of Scanning}
\begin{itemize}
    \item Port Scanning\\
        Sending packets to a target computer with the intent of learning about the port status.
    \item Network Scanning\\
        Locate mostly all live hosts on a network.
    \item Vulnerability Scanning\\
        Used to identify weaknesses or vulnerabilities on a target system.
\end{itemize}
\subsection{Port Scanning}

Port scanning program / tool report:
\begin{itemize}
    \item Open Ports
    \begin{itemize}
        \item Allows access to applications / services and can be vulnerable to attack.
    \end{itemize}
    \item Closed Ports
    \begin{itemize}
        \item Does not allow entry or access to a service.
    \end{itemize}
    \item Filtered Ports
    \begin{itemize}
        \item Open, but might indicate that a firewall is being used to allow specified traffic into or out of the network, through that port.
    \end{itemize}
\end{itemize}

Is port scanning legal> Some states / countries consider it legal.

\subsubsection{Types of port scans}
\begin{enumerate}
    \item Connect Scan (Full-open scan)
    \begin{itemize}
        \item Utilizes three way handshake
        \item Completed handshake indicates open port
        \item 
    \end{itemize}
    \item SYN scan (Half scan)
    \begin{itemize}
        \item Starts like a full scan but does not complete the final step of the handshake.
        \item Lower chance of being logged.
    \end{itemize}
    \item FIN scan
    \item XMAS Scan
    \begin{itemize}
        \item All flags enabled, combination of flags is illogical and illegal.
        \item 
    \end{itemize}
    \item NULL Scan
    \item ACK scan
\end{enumerate}

\subsection{Network Scanning}
Network scannign is for checking live hosts.
\begin{enumerate}
    \item Wardialing is the other forms of scanning in that it simply dials a block of phone number using a standard modem to locate systems that also have a modern attached and accept connections.
    Modems are still in use so a hacker can use
    \item pinging
    \item ping sweep
\end{enumerate}

\subsection{Vulnerability Scanning}

\subsection{Banner Grabbing}

\subsection{Scanning anonymity using proxy}

\subsection{Mapping the network}

\subsection{Packet crafting and manipulation}