\subsection{Multiple choice questions}
\begin{enumerate}
    \item Enumeration is useful to system hacking because it provides: \textbf{\left( Usernames \right))}
    \item How would you use Netcat to set up a server on a system? \textbf{\left( \verb|NC -l -p 1000| \right))}
    \item \verb|____| is the process of exploiting a system. \textbf{\left( System Hacking \right))}
    \item How is a brute-force attack performed? \textbf{\left( By trying all possible combinations of characters \right))}
    \item A \verb|_____| is a type of offline attack. \textbf{\left( Hashing attack \right))}
    \item An attacker can use a \verb|_____| to return to a compromised system. \textbf{\left( Backdoor \right))}
    \item A \verb|_____| is used to represent a password. \textbf{\left( Hash \right))}
    \item What utility may be used to stop auditing or logging of events? \textbf{\left( Auditpol \right))}
    \item Which of the following is a utility used to reset passwords? \textbf{\left( Trinity Rescue Kit \right))}
    \item A good defence against password guessing is \verb|_____|. \textbf{\left( Complex passwords \right))}
    \item In which phase within the ethical hacking framework od you alder or delete log information. \textbf{\left( Covering tracks. \right))}
    \item In what phase is an attacker who is currently conducting a successful man-in-the-middle attack? \textbf{\left( Passive Online \right))}
    \item Being part of security team, receive a ticket from one of your users that their computer is periodically slow and also states that from time to time, documents have either disappeared or have been moved from their original location. You logs remote desktop to the user’s computer investigate. Where is the most likely place to see? \textbf{The processes tab in Task Manager}
    \item Which of the following tools allows you to perform password cracking? \textbf{Cain \& Abel}
    \item A \verb|_____| is a file used to store passwords in Windows. \textbf{SAM} 
    \item \verb|_____| is a hash system used to store passwords in older Windows systems. \textbf{LM} 
    \item \verb|_____| is used to partially encrypt the SAM. \textbf{SYSKEY} 
    \item Which hashing system should be used instead of LM or NTLM? \textbf{Kerberos} 
    \item NTLM provides what benefit vs LM? \textbf{Security} 
    \item ADS (alternate data streams) requires what to be present? \textbf{NTFS} 
    \item On newer Windows system, what hashing mechanism is disabled? \textbf{LM} 
    \item If a domain controller is not present, what can be used instead? \textbf{NTLMv2} 
    \item Alternate data streams are supported in which file system? \textbf{NTFS}
    \item This protocol is used for email purpose; it sends cleartext usernames and passwords with no forms of encryption or a means of challenging. What authentication protocol is this? \textbf{POP}  
\end{enumerate}

\subsection{Brief Answer questions}
\begin{enumerate}
    \item Explain "Types of Password Cracking processes"
    \begin{itemize}
        \item Passive Online
        \begin{itemize}
            \item Sniffing
            \item Man in the middle
        \end{itemize}
        Monitor network for packets that contain unsecured passwords.
        Some of these protocols are Telnet, HTTP, SNMP, POP, etc.
        \item Active Online
        \begin{itemize}
            \item Guessing
            \item Keylogger
            \item Spyware
        \end{itemize}
        Require direct interaction with the system.
        \item Offline
        \begin{itemize}
            \item Rainbow Tables
            \item Brute force
        \end{itemize}
        Attacks the way passwords are stored.
        \item Nontechnical
        \begin{itemize}
            \item Social Engineering
        \end{itemize}
        Tries to retrieve the password directly from the user.
    \end{itemize}
    \item Describe features / steps of any one tool for Password cracking process.
    \begin{itemize}
        \item \verb|wintrgen| tool will generate a rainbow table following specific parameters like size and hash format.
        \item 
    \end{itemize}
    
\end{enumerate}

