The first instance we see of abolishing slavery was the Emancipation Proclamation, the main use however was to bolster the Union's moral and numbers.
The proclamation freed only enslaved people in areas of rebellion, and because they were rebelling against the Unions view on slavery, they did not follow through was what Lincoln proposed.
Also, the Emancipation Proclamation left hundreds of thousands of slaves in bondage in Union-occupied.

On January 31, 1865 Congress legally abolished slavery ''except as punishment for a crime whereof the party shall have been duly convicted.''
This would free four million people from the bonds of slavery that had existed in North America for 250 years. %\cite{13thAmendment}

After Lincoln was assassinated, Andrew Johnson took his position as president and was the leader for the policies of the Reconstruction.
Johnson, being an unapologetic racist from Tennessee, was much more lenient towards the South than Northerners would have preferred.
Pardoning all Southerners except wealthy ones in the hope that different people would replace the wealthy leaders in the South.
Because of Johnson's more gentle views of managing the South during the Reconstruction, many southern governments were able to enforce antebellum views on African Americans once again.

After the civil war, many former enslavers tried to maintain control over their laborers by offering them sharecropping contracts.
By dividing their land and renting it to former slaves, they would keep their income and still utilize the land that they owned.
Land owners would often take advantage of less educated slaves by inflating the prices of materials and taxing more than was necessary.
Sharecroppers would fall into debt and it would be very difficult to get out of the contract.
Colonel P.H.\ Anderson of Tennessee was one of these former slave owners, trying to lure Jourdon back into his service by "promising to do better for [Jourdon] than anybody else can."
Jourdon, doing tolerably well away from his former master, making a wage, a home, and schooling for his children, does not want to return to the service of the Colonel.
Jourdon decides to add some sarcasm to his reply by asking for what wages the Colonel will be supplying as well as a token of sincerity from the Colonel being the sum of wages from the labors of the past including interest.
The sum the Jourdon is asking for was \$11,680 between his wife and himself.
Jourdon knows that this sum is more than the Colonel will ever pay and is more of a slight at how much his years of servitude earned the Colonel that could have been his.
You can assume that Jourdon is upset that the Colonel asked for Jourdon to return, but is to polite to reply back with harsh words.

The Mississippi Black Codes is one of the most important and efficient methods that whites used to reassert their dominance over freed slaves.
The good aspects of the Black Codes gave African Americans the right to sue and be sued, acquire personal property, and negotiate contracts.
The bad implications of the Black Codes are much more numerous and far-reaching.
Blacks cannot carry firearms or knives without permission from the police or the military, they cannot gather groups, with or without whites present.
Blacks are forced to show proof of employment or risk being arrested for vagrancy and sold into a labor contract to anyone willing to buy them, if they quit their job, they are to be arrested and returned to their master.
Also, if convicted of a crime and unable to pay the associated fees or taxes, they are convicted of vagrancy and sold into labor.

While the Black Codes do give former slaves some freedoms, overall it was drafted as a means to control blacks and reassert white supremacy.
Some references say that the conditions of contracted labor was worse than that of slavery because during slavery, the wealth of the master was determined by how many slaves he owned.
With the ease that people could falsely convict blacks to get them sold labor was much cheaper than it had been when farmers needed to own slaves.
So owners of convict laborers would treat their workers worse than if they had owned them.

