{\it Oryx and Crake} is a science fiction novel by Margaret Atwood.
The book describes a world through the eyes of Snowman/Jimmy after genetic engineering has developed to far and toppled the human race.
Atwood uses imagery to describe the horrors that Snowman/Jimmy has seen in the forms of experiments gone wrong, or his fairly messed up childhood in the Compounds.

The novel begins with the last known human waking up and describing the situation he is in and the state of the apocalypse.
"Out of habit he looks at his watch -- stainless-steel case, burnished aluminum band, still shiny although it no longer works." \autocite[3]{atwood1}
This shows that whatever apocalyptic event did not happen to long ago, Snowman's watch is still shiny and he still has the habit of checking it, even though it gives him anxiety.

Atwood utilizes flashbacks from Snowman's perspective to show how the world was before the disaster, and how the disaster came to pass.
Jimmy used to live in various compounds, which was were the smarter people lived and worked for genetic-related corporations.
Jimmy's dad relates the compounds to castles, saying "Castles were for keeping you and your buddies safe inside and for keeping everybody else outside." \autocite[28]{atwood1}
This idea forms a dichotomy between the compounds and the rest of society, which they refer to as "pleeblands."
Outside the compounds is seen as lawless and wild, where "you could get things out there you couldn't get in here." \autocite[64]{atwood1}
Most of the things referred to in this manner are sexual in nature and usually highly graphic.

After Jimmy meets his friend Greg, later Crake, they would play video games in Crakes room that were strategic in nature but had villainous undertones.
In the game Blood and Roses, the goal was to trade atrocities for human achievements.
"To do this you needed to know the numbers – the total number of corpses for the atrocities, the latest open-market price for the artworks; or, if the artworks had been stolen, the amount paid out by the insurance policy.
It was a wicked game." \autocite[79]{atwood1}
This gives some foreshadowing into the story later, when Crake creates his "children."
Crake's children were supposed to fix all of the things wrong with humans but they also caused a plague that wiped out the population.
So Crake's children are both the best of humanities achievements and the worst of its atrocities.