After the reconstruction of the south whites were trying to return to their place of power that they had lost after the Civil War.
During the later half of the 1800's, whites used many means to put blacks back into subservient positions, including the elimination of black voting, segregation, convict labor, and lynching.

15th amendment banned stripping someone from the right to vote based on ethnicity, or former slave. 
To get around this the south placed a poll tax that was heigh enough to deter poor blacks from voting.
Literacy and constitutional understanding tests were also introduced that were very difficult for the uneducated to pass, even some whites were declined the right to vote.
Because of these, black voting had been virtually eliminated by 1906.

Segregation was not about separation, it was about domination. 
Blacks and whites interacted frequently in their day to day lives, blacks were expected to play the inferior role, like cooking and cleaning for whites. 
Virtually all institutions were segregated with the blacks side being inferior to the whites.
White south does not desire or intend to ever include black men to be counted as citizens, in there eyes blacks were just laborers to be treated harshly.

Individuals convicted of crimes could be sold to private citizens for labor.
Crimes were often minor or fake with multiple charges to increase the sentence.
It was against the law to quit your job before contracted time was over or you would be charged with vagrancy (not having a job or proof of wealth).
Conditions for convict laborers were worse than slavery because a slave would have a monetary value to the owner, but convict laborers were only under contract and could be replaced cheaply by bribing the sherifs and judges.

Lynching, where groups of private citizens would execute someone without legal authority.
These could be actual or accused criminals (black or white), black men that had slept with white women, or blacks that had challenged white supremacy.

The actions and laws that whites implemented gave the illusion of slavery and forced blacks into subservient positions.
Blacks were afraid to leave areas where they were known or would have to have a white person protect them from being lynched or sold as a convict laborer.