\begin{problem}{\#1 (7 points)}
    \begin{enumerate}[label=\alph*)]
        \item Consider the language \(S^*\), where \(S = \{a,ab,ba\}\). Is the string \((abbba)\) a word in the language?
        \item Write out all of the words in this language with 3 letters.
        \item Write 5 words from this language with 4 letters.
        \item What is English description of this language?
    \end{enumerate}
\end{problem}
\vspace{2em}
\begin{solution}
    \begin{enumerate}[label=\alph*)]
        \item The String \((abbba)\) is not in the language \(S^*\).\\
        If we factor the word we get: \(ab|b|ba\) and \(b\) is not a letter in the alphabet, meaning that this cannot be a word in \(S^*\).
        \item \((aaa, aab, aba, baa)\)
        \item \((aaaa, aaab,aaba,abaa,baaa,abba)\)
        \item All words of a's, and b's with no more than 2 b's in a row. 
    \end{enumerate}
\end{solution}

\begin{problem}{\#2 (6 points)}
    Let \(\Sigma = \{a,b\}\)
    \begin{enumerate}[label=\alph*)]
        \item Consider the language \(S^*\), where \(S=\{aa,ab,ba,bb\}\).
        Give an English description of this language.
        \item Give an example of a set \(S\) such that \(S^*\) only contains all possible strings of a's and b's that have length divisible by 3.
        \item Let \(S\) be all strings of a's and b's with odd length.
        What is \(S^*\)?
    \end{enumerate}
\end{problem}
\vspace{2em}
\begin{solution}
    \begin{enumerate}[label=\alph*)]
        \item All combinations of a's and b's excluding odd amounts of just a's or odd amounts of just b's.
        \item \(S=\{aaa,aab,aba,abb,baa,bab,bba,bbb\}\), with a language of only three letter words the Kleene closure is guaranteed to only have combinations divisible by 3.
        \item \(S^*\) is all strings of a's and b's.
        Because there is a single 'a' and 'b', any string in \(S^*\) could be factored with these two. 
    \end{enumerate}
\end{solution}

\begin{problem}{\#3 (10 points)}
    \begin{enumerate}[label=\alph*)]
        \item Let \(S=\{b,bb\}\) and \(T=\{ab,bb,bbbb\).
        Show that \(S^* = T^*\).
        \item Let \(S=\{ab,bb\}\) and \(T=\{ab,bb,bbb\}\).
        Show that \(S^* \neq T^*\) but that \(S^* \subset T^*\)
        \item What principle does this illustrate?
    \end{enumerate}
\end{problem}
\vspace{2em}
\begin{solution}
    \begin{enumerate}
        \item \(bbbb \in T\) can be factored by \(bb \in S\).
        Therefore, any combination of \(bbbb\) is a combination of \(bb\) meaning that \(S^* = T^*\).
        \item Because \(S \subset T\) then by definition, every word in \(S^*\) is in \(T^*\), but not every word in \(T^*\) is in \(S^*\).
        The word \(ab|bbb \in T^*\) but this cannot be factored with only \(ab,bb\) so \(ab|bbb \notin S^*\).
        \item This shows the principle of equality of sets.
    \end{enumerate}
\end{solution}

\begin{problem}{\#4 (15 points)}
    Let \(\Sigma=\{a,b\}\).
    Give recursive definitions for the following languages over \(\Sigma\).
    \begin{enumerate}[label=\alph*)]
        \item The language BB of all words containing the substring \(bb\).
        \item The language NOTBB of all words not containing the substring \(bb\).
        \item Give recursive definition of the set EVEN.
        Show that all the numbers in it end in the digits 0, 2, 4, 6, or 8.
        \item Give a recursive definition of the set \(\text{ODD}=\{1,3,5,7,\ldots\}\).
        \item Give a recursive definition for the set of strings of digits 0,1,2,3,\ldots, 9 that cannot start with the digit 0.
    \end{enumerate}
\end{problem}
\vspace{2em}
\begin{solution}
    \begin{enumerate}[label=\alph*)]
        \item BB is defined by the rules:
        \begin{enumerate}[label=\arabic*]
            \item The string \(bb\) is in BB.
            \item If \(x\) is in BB, any string of a' or b's concatenated with \(x\) is in BB.
            \item The only elements of BB are those that are constructed by following rules 1 and 2.
        \end{enumerate}
        \item NOTBB is defined by the rules:
        \begin{enumerate}[label=\arabic*]
            \item \(a \in \text{NOTBB}\) and \(b \in \text{NOTBB}\)
            \item If \(x \in \text{NOTBB}\) and \(x\) ends with \(a\), add \(a\) or \(b\).
            If \(x\) ends with \(b\) add \(a\).
            \item The only elements in NOTBB are the ones that are constructed by following rules 1 and 2
        \end{enumerate}
        \item EVEN is defined by the rules:
        \begin{enumerate}[label=\arabic*]
            \item \(2 \in \text{EVEN}\)
            \item If \(x \in \text{EVEN}\), \(x+2 \in \text{EVEN}\).
            \item The only elements in EVEN are the ones that are constructed by following rules 1 and 2.
        \end{enumerate}
        \(\text{EVEN} = \{2,4,6,8,10,12,\ldots\}\), any element of EVEN will end in \((0,2,4,6,8)\).
        \item ODD is defined by the rules:
        \begin{enumerate}[label=\arabic*]
            \item \(1 \in \text{ODD}\)
            \item If \(x \in \text{ODD}\), \(x+2 \in \text{ODD}\)/
            \item The only elements in ODD are the ones that are constructed by following rules 1 and 2.
        \end{enumerate}
        \item String of digits not starting with 0 is defined by the rules:
        \begin{enumerate}[label=\arabic*]
            \item \((1,2,3,4,5,6,7,8,9) \in \text{DIGITS}\)
            \item If \(w\) is any word in DIGITS, then the concatenations:\\\(w0,w1,w2,w3,w4,w5,w6,w7,w8,w9\) are also in DIGITS.
            \item The only elements in DIGITS are the ones that are constructed by following rules 1 and 2.
        \end{enumerate}
    \end{enumerate}
\end{solution}

\begin{problem}{\#5 (5 points)}
    In the given recursive definition for the language PALINDROME over the alphabet \(\Sigma = \{a,b\}\):
    \begin{enumerate}
        \item \(a, b \in \text{PALINDROME}\)
        \item if \(x\) is in PALINDROME, then \(axa\) and \(bxb\) are also in PALINDROME.
    \end{enumerate}
    All the words in the language defined above have an odd length and so it is not all of PALINDROME.
    Fix this problem.
\end{problem}
\vspace{2em}
\begin{solution}
    Adding \(aa\) and \(bb\) to the base case will fix the odd length issue.
    \(aa\) and \(bb\) will create only even members of PALINDROME, \((aa,bb,aaaa,baab,abba,bbbb,\ldots)\).
    The combination of even PALINDROME and odd PALINDROME creates a complete set of PALINDROME. 
\end{solution}