\documentclass[12pt]{article}
\usepackage[top=1in, bottom=1in, left=1in, right=1in]{geometry}
\usepackage[onehalfspacing]{setspace}
\usepackage[none]{hyphenat} % This command prevents hyphenation of words

\usepackage{hyperref}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage{csquotes}

\usepackage[
style=mla-new,
showmedium=false
]{biblatex}
\addbibresource{debate.bib}
\DeclareBibliographyAlias{misc}{article}
\begin{document}
% This is the Header
% Make sure you update this information!!!!
\noindent
\textbf{LEMIT} \hfill \textbf{Brandon Thompson} \\
\normalsize Prof. LeFrancois \hfill Due Date: 6/15/2020 \\

% This is where you name your homework
\begin{center}
\textbf{Debate: Cryptocurrency as legal tender?}
\end{center}
	
	Good afternoon ladies and gentlemen, today I am going to describe why Bitcoin is 
	not a viable method of worldwide legal tender. Firstly Bitcoin does not conform to
	classical properties of a currency. Successful currency has three main properties,
	the currency functions as a medium of exchange, a unit of account, and a store of
	value. Medium of exchange means that those who possess it can participate as an equal
	market player. Producers know what to produce and how much to charge, and consumers
	can budget accordingly.\autocite{med}
	A unit of account is a standard monetary unit of measurement
	of value/cost of goods, services or assets.
	\autocite{unit}
	A store of value is an asset that
	maintaining its value without depreciating such as gold and other precious metals.
	\autocite{store}
	Bitcoin struggles to meet any of these three criteria to be a successful currency.
	Secondly, traditional currency is susceptible to counterfeiting but mass counterfeiting
	requires a lot of resources as well as geographical location for operation and
	distribution. Counterfeit cryptocurrency requires less resources and thus may be
	more at risk for mass counterfeit operations. 
	Thirdly, Bitcoin influences illegal activities on websites that follow
	the Silk Road example because of the anonymity designed into Bitcoin transactions.
	Fourth, because of the high market volatility, investing in Bitcoins can have very
	negative side effects for investors should the user base decline.

	Bitcoins lack as a medium of exchange because of the difficulty of getting new bitcoin.
	Bitcoins are introduced through 'mining' where miners solve difficult mathematical
	problems. The user that solves the problem is rewarded with a Bitcoin, and the difficulty
	of the problems increases for each bitcoin introduced. The mining industry is dominated 
	by supercomputers and crowd-mining operations that are require large capital
	investments, so for a typical consumer to acquire bitcoins they need to be traded at an
	online exchange and store them in an online account. These purchases of bitcoins
	typically require a direct bank transfer and often have
	low liquidity, high bid-ask spreads, and some execution and custody risks associated
	with the transaction. Meaning that there is no standard asking price, anyone that has
	bitcoins can offer to trade them for as much or as little as they want.
	Lastly bitcoins are not a viable medium of exchange because transactions require a
	verification process
	that takes a few minutes, meaning longer time is spent on a transaction versus
	traditional currency. Secondly, Bitcoins are not a useful unit of account because 
	its extreme volatility.
	The value of a bitcoin changes greatly from a day to day basis and the changing prices
	can cause merchants to lose money, and confuse the customer. Another issue is the price
	of a bitcoin is far greater than that of an ordinary product, this means that the cost
	is displayed in four or more decimal places. This is likely to confuse consumers, as
	well as accounting software that currently does not account for large decimal values
	and fluctuation of values.
	As a store of value, bitcoin suffers because there is no physical manifestation of
	the currency, instead of hiding bitcoins under the mattress or putting them into a bank,
	they need to
	be kept in online accounts called ''digital wallets''. Security of digital wallets has
	been a major difficulty for the industry. Once the consumer finds a way to obtain and
	secure bitcoins, there is a measure of risk in holding them because of the volatility.
	If you put money into a bank, you are guaranteed that you are able to withdraw that
	same amount, with large daily changes in market prices, bitcoins are more of a high
	risk investment than a currency.\autocite{chap2}

	Counterfeiting traditional currency is difficult because of security threads in paper
	bills, watermarks, tricky images, color changing ink, and special paper. Mass
	counterfeit operations are also limited by geography, they need a place to
	manufacture the currency and transport the
	currency to where it is viable. Countermeasures for cryptocurrency include security
	from hackers, cryptographic capabilities within software and virtual wallets.
	Counterfeiting cryptocurrency requires less resources and bypasses the geographic
	boundary, because the nature of cryptocurrency is virtual and traded online. This
	means that cryptocurrency could be at a much greater risk for counterfeit, which
	would diminish the effectiveness of the currency because one of the main factors
	that attributed to the success thus far is that there are a limited number of
	Bitcoins available.\autocite{chap8} 

	Bitcoin is a major contributor, if not directly, to illegal websites like the
	Silk Road that traded more than 23,000 illegal items, 1.22 million USD monthly in
	2012. The anonymity of bitcoin transactions is paramount in the success of
	illegal websites so that the users of the website are not tracked through financial
	information.\autocite{chap12}

	Lastly, Bitcoin has no intrinsic value, the worth of a bitcoin is determined by its
	usefulness as a currency. This means that as the hype factor diminishes, investors
	that hold a lot of the money will see significant loss in their investments. If the
	user base declines and people trade out their coins, the owner base will diminish
	and if 51\% of the owner base  want to change something, they can modify the code
	however they want. Before i mentioned that there are a set number of bitcoins to be
 	distributed, this number can be altered if 51\% of the owners decide that
	a change is necessary.\autocite{chap13}

	Bitcoin should not be a worldwide method of legal tender because it does not have
	the properties of a successful currency, there are greater risks of counterfeit
	operations, Anonymity promotes illegal activity and high market volatility make
	for bad exchange rates. Thank you.

	\clearpage
	\printbibliography
\end{document}
