\subsection{Role of computers in crimes}
\begin{itemize}
    \item Computers can be the \textbf{target} of a crime.
    \item The \textbf{instrument} of a crime.
    \item The \textbf{evidence repository} storing valuable information about the crime.
\end{itemize}

Depending on the role of the computer in the crime, either a target an instrument or a storage location, the forensic analyst will check different locations.

Cybercrime is increasing because the internet has made targets more accessible, the risks are much lower than traditional crimes.
Any cyber crime is possible from any remote site.

\subsection{Cyber crimes}
\begin{enumerate}
    \item Identity theft
    \item Hacking systems for data
    \item Cyber stalking and harassment
    \item Internet fraud
    \item Non-access computer crimes
    \item Cyberterrorism
\end{enumerate}

\subsubsection{Identity theft}
Identity theft is any use if another person's Identity, without and with knowledge or permission of that person, typiclly to commit financial fraud.

There are three common methods to perpetrate identity theft:
\begin{enumerate}
    \item Phishing
    \item Spyware
    \item Discarded information
\end{enumerate}

\subsubsection{Hacking Systems for data}
\begin{enumerate}
    \item SQL Injection
    \begin{itemize}
        \item 
    \end{itemize}
    \item Cross-Site Scripting
    \begin{itemize}
        \item Look for any scripts in the website that are not coded by the websites programmers.
        \item Search the web server's logs for any redirect messages, then determine if any of these redirects cannot be accounted for via legitimate web coding.
    \end{itemize}
    \item Password Cracking
    \begin{itemize}
        \item after cracking the password, typically a reboot is required, so the investigator could look for reboots followed by an administrator login.
        \item Physical security
    \end{itemize}
    \item tricking tech support
    \begin{itemize}
        \item First attacker writes script into the startup folder to create a new administrator.
        \item Investigator should look for any unrecognized scripts.
    \end{itemize}
\end{enumerate}

\subsubsection{Cyber Stalking}
Use of electronic communications to harass to threaten another.
Investigators will ask three questions:
\begin{enumerate}
    \item Is it possible?
    \item How frequent? One time is not stalking, repeated behavior is.
    \item How serious? Specific and serious threats are more concerning.
\end{enumerate}

\subsubsection{Fraud}
Fraud is a broad category of crime that can encompass many different activities.